Unshuffling Permutations

### 2016-02-03 new-article.tex
Lemma 3 (statement completed)

\begin{lemma}
  \label{lemma:at most one edge monotone}
  Let $\pi = \pi_1 \, \sigma_1 \, \pi_2 \, \sigma_2 \, \pi_3$
  be a permutation with $|\sigma_1| \geq 2$ and $|\sigma_2| \geq 2$,
  and $\vv{\mathcal{M}}$ be an oriented perfect matching of $G_\pi$
  that avoids
  \InclusionLL,~\InclusionLR,~\InclusionRL,~\InclusionRR,~\CrossingLR
  and \CrossingRL, and such that for any two distinct arcs $(a, a')$ and
  $(b, b')$ in $\vv{\mathcal{M}}$ we have $\pi(a) < \pi(b)$ if and only
  if $\pi(a') < \pi(b')$.
  The following assertions hold:
  \begin{enumerate}
    \item
    If $\sigma_1$ is increasing, $\sigma_2$ is decreasing, and
    $\sigma_1$ is above $\sigma_2$
    (see Fig.~\ref{subfig:increasing before and above decreasing}),
    then $\vv{\mathcal{M}}$ contains either at most one
    $(\sigma_1, \sigma_2)$-arc or at most one
    $(\sigma_2, \sigma_1)$-arc.
    \item
    If $\sigma_1$ is decreasing, $\sigma_2$ is increasing, and $\sigma_1$
    is below $\sigma_2$
    (see Fig.~\ref{subfig:decreasing before and below increasing}),
    then $\mathcal{M}$ contains at most one
    $(\sigma_1, \sigma_2)$-edge.
  \end{enumerate}
\end{lemma}

>>>>

\begin{lemma}
  \label{lemma:at most one edge monotone}
  Let $\pi = \pi_1 \, \sigma_1 \, \pi_2 \, \sigma_2 \, \pi_3$
  be a permutation with $|\sigma_1| \geq 2$ and $|\sigma_2| \geq 2$,
  and $\vv{\mathcal{M}}$ be an oriented perfect matching of $G_\pi$
  that avoids
  \InclusionLL,~\InclusionLR,~\InclusionRL,~\InclusionRR,~\CrossingLR
  and \CrossingRL, and such that for any two distinct arcs $(a, a')$ and
  $(b, b')$ in $\vv{\mathcal{M}}$ we have $\pi(a) < \pi(b)$ if and only
  if $\pi(a') < \pi(b')$.
  The following assertions hold:
  \begin{enumerate}
    \item
    If $\sigma_1$ is increasing, $\sigma_2$ is decreasing, and
    $\sigma_1$ is above $\sigma_2$
    (see Fig.~\ref{subfig:increasing before and above decreasing}),
    then $\vv{\mathcal{M}}$ contains either at most one
    $(\sigma_1, \sigma_2)$-arc or at most one
    $(\sigma_2, \sigma_1)$-arc.
    \item
    If $\sigma_1$ is decreasing, $\sigma_2$ is increasing, and $\sigma_1$
    is below $\sigma_2$
    (see Fig.~\ref{subfig:decreasing before and below increasing}),
    then $\mathcal{M}$ contains at most one
    $(\sigma_1, \sigma_2)$-arc or at most one $(\sigma_2, \sigma_1)$-arc.
  \end{enumerate}
\end{lemma}
